---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
should_eval <- 
  rlang::is_installed("xgboost") && 
  rlang::is_installed("parsnip") &&
  rlang::is_installed("callr")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = should_eval
)
```

# bundle

_NOTE: This package is very early on in its development and is not yet minimally functional._

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/bundle)](https://CRAN.R-project.org/package=bundle)
[![Codecov test coverage](https://codecov.io/gh/simonpcouch/bundle/branch/main/graph/badge.svg)](https://app.codecov.io/gh/simonpcouch/bundle?branch=main)
[![R-CMD-check](https://github.com/simonpcouch/bundle/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/simonpcouch/bundle/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

R holds most objects in memory. However, some models store their data in locations that are not included when one uses `save()` or `saveRDS()`. bundle provides a common API to capture this information, situate it within a portable object, and restore it for use in new settings.

## Installation

You can install the development version of bundle like so:

``` r
pak::pak("simonpcouch/bundle")
```

## Example

bundle prepares model objects so that they can be effectively saved and re-loaded for use in new R sessions. To demonstrate using bundle, we will train a boosted tree model, bundle it, and then pass the bundle into another R session to generate predictions on new data.

First, loading needed packages:

```{r example, message = FALSE, warning = FALSE}
library(bundle)
library(parsnip)
library(callr)
```

Fitting the boosted tree model:

```{r}
# fit an boosted tree with xgboost via parsnip
mod <-
    boost_tree(trees = 5, mtry = 3) %>%
    set_mode("regression") %>%
    set_engine("xgboost") %>%
    fit(mpg ~ ., data = mtcars[1:25,])

mod
```

Now that the model is fitted, we'll prepare it to be passed to another R session by bundling it:

```{r}
# bundle the model
bundled_mod <-
  bundle(mod)

bundled_mod

```

Passing the model to another R session and generating predictions on new data:

```{r}
# load the model in a fresh R session and predict on new data
r(
  func = function(bundled_mod) {
    library(bundle)
    library(parsnip)
    
    unbundled_mod <- 
      unbundle(bundled_mod)

    predict(unbundled_mod, new_data = mtcars[26:32,])
  },
  args = list(
    bundled_mod = bundled_mod
  )
)
```

For a more in-depth demonstration of the package, see the main vignette with:

```{r}
vignette("bundle")
```

## Code of Conduct
  
Please note that the bundle project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
