---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

should_eval <- rlang::is_installed("xgboost") && rlang::is_installed("parsnip")
```

# gift

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/gift)](https://CRAN.R-project.org/package=gift)
<!-- badges: end -->


R holds most objects in memory. However, some models store their data in locations that are not included when one uses `save()` or `saveRDS()`. gift provides a common API to capture this information, situate it within a portable object, and restore it for use in new settings.



## Installation

You can install the development version of gift like so:

``` r
pak::pak("simonpcouch/gift")
```

## Example

A common use case for serialization in R is the storing of model objects for later use in prediction tasks. For instance, we can train a boosted tree model, serialize it, and then later load it into another R session to generate predictions on new data:

```{r example, eval = should_eval}
library(gift)
library(parsnip)

mod <-
    boost_tree(trees = 5, mtry = 3) %>%
    set_mode("regression") %>%
    set_engine("xgboost") %>%
    fit(mpg ~ ., data = mtcars[1:20,])

wrapped_mod <-
  wrap(mod)

unwrapped_mod <- 
  unwrap(wrapped_mod)

preds <-
  predict(unwrapped_mod, new_data = mtcars[21:32,])

preds
```


